---
title: "PS3"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

### load libraries
```{r}
library(ggplot2)
library(dplyr)
library(statsr)
library(tidyr)
```

# Author: Pinlu Chen
# Github repository: https://github.com/pinlu-chen/Problem-Set-3


# Abstract

### Established in 1985, the Canadian General Social Survey (GSS) programm was developed as a series of independent annual voluntary intersectoral surveys, each covering a single topic. The overall objectives of the programm were and continue to be to collect data on social trends in order to monitor changes in the living conditions and well-being of Canadians, and to provide information on specific social policy issues.
###
### Recent surveys of GSS programs focused on seven topics: life at work and at home; families; care and receiving care; giving, volunteering and participating; victimization; social identity and time use.
###
### In this paper we analyze the most recent accessible GSS data and apply statistical models.

# Introduction

### The General social survey collects information from people aged 15 and older in ten provinces of Canada, with the exception of permanent residents in institutions. The victimization cycle, last collected in 2009 and 2014, was also conducted in the territories of Canada.
###
### The sample size for CSS has changed over time. Prior to 1998, the target final sample size for each GSS cycle was approximately 10,000. This figure was increased in 1999 to a target of 25,000 people until 2015, when this figure was reduced to 22,000 people, and then further reduced to 20,000 people starting in 2016.

# Data

### First, we clean the downloaded GSS data by using the given R script

```{r, include=FALSE}
source("gss_cleaning.R", local = knitr::knit_global())
```

### After cleaning the downloaded GSS data, we load the clean gss.csv into R dataframe

```{r}
df <- read.csv("gss.csv")
```


### Display some rows
```{r}
head(df)
```

### Let's check all the column names in the dataset
```{r}
names(df)
```

### As we see there are 81 total columns.


### Data Summary
```{r}
summary(df)
```


# Model

### We construct linear regression model between the following variables: income ~ age, education, sex, province, occupation


```{r}
###model <- lm(income_family ~ age + education + sex + province + occupation, data = df)
```

# Results

```{r}
summary(df$age)
```

```{r}
table(df$sex)
```

```{r}
ggplot(data = df) +
  geom_bar(mapping = aes(x = sex))
```





# Number of respondents per province
```{r}
table(df$province)
```

```{r}
ggplot(data = df) +
  geom_bar(mapping = aes(x = province)) +
  theme(axis.text.x = element_text(angle = 90))
```

```{r}
ggplot(data = df) +
  geom_boxplot(mapping = aes(x = reorder(province, age, FUN = median), y = age)) + 
  theme(axis.text.x = element_text(angle = 90))
```


### Education status of respondents
```{r}
table(df$education)
```

```{r}
ggplot(data = df, mapping = aes(x = age, colour = education)) +
  geom_freqpoly(binwidth = 0.1)
```

```{r}
ggplot(data = df) +
  geom_count(mapping = aes(x = education, y = sex)) +
  theme(axis.text.x = element_text(angle = 90))
```

```{r}
table(df$occupation)
```

```{r}
ggplot(data = df) +
  geom_bar(mapping = aes(x = occupation)) +
  theme(axis.text.x = element_text(angle = 90))
```

```{r}
ggplot(data = df) +
  geom_point(mapping = aes(y = education, x = occupation)) + 
  theme(axis.text.x = element_text(angle = 90))
```

```{r}
ggplot(data = df) +
  geom_point(mapping = aes(x = province, y = occupation)) + 
  theme(axis.text.x = element_text(angle = 90))
```

```{r}
table(df$aboriginal)
```

```{r}
ggplot(data = df) +
  geom_point(mapping = aes(x = aboriginal, y = occupation)) + 
  theme(axis.text.x = element_text(angle = 90))
```

```{r}
ggplot(data = df) +
  geom_point(mapping = aes(x = aboriginal, y = education)) + 
  theme(axis.text.x = element_text(angle = 90))
```

### Relationship between income and age
```{r}
ggplot(data = df) +
  geom_point(mapping = aes(x = income_family, y = age)) + 
  theme(axis.text.x = element_text(angle = 90))
```

### Relationship between income and sex
```{r}
ggplot(data = df) +
  geom_point(mapping = aes(x = income_family, y = sex)) + 
  theme(axis.text.x = element_text(angle = 90))
```

### Relationship between income and province
```{r}
ggplot(data = df) +
  geom_point(mapping = aes(x = income_family, y = province)) + 
  theme(axis.text.x = element_text(angle = 90))
```

# Discussion

### We see that minimum age of the respondents is 15, mean age is 52.19, and maximum age is 80.

### We see that there are overall 11203 female respondents and 9388 male respondents.

# References

### Statistics Canada https://www150.statcan.gc.ca/n1/pub/89f0115x/89f0115x2019001-eng.htm
